Modeling costs and benefits of genomic wastewater surveillance

### 2023-05-04 paper/model-documentation.qmd
pushing latest version of model documentation

---
title: Modeling costs and benefits of genomic wastewater surveillance
subtitle: Model appendix draft
#author:
#  - name: Pedro Nascimento de Lima
#    email: plima@rand.org
#    affiliations: 
#        - id: rand
#          name: RAND Corporation
#          department: Engineering and Applied Sciences
#          address: 1776 Main Street
#          city: Santa Monica
#          state: CA
#          postal-code: 90401
#    attributes:
#        corresponding: true
#  - name: and colleagues
#    email: others@rand.org
#    affiliations:
#        - ref: rand
abstract: |
  Introduces a model to assess the value provided by wastewater genomic surveillance network. This document is meant to be used as a supplementary appendix of the paper.
keywords: 
  - Genomic Surveillance
  - Pandemic Response
date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      #name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: super
  elsevier-html:
    keep-tex: true
    journal:
      #name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: super
  docx:
      cite-style: super
---

@@

Genomic surveillance might provide an early signal to decision makers by providing information about current disease prevalence, hence effectively reducing $a$. One might also represent genomic surveillance using a mechanistic formulation where

>>>>

---
title: Modeling costs and benefits of genomic wastewater surveillance
subtitle: Supplementary appendix draft
#author:
#  - name: Pedro Nascimento de Lima
#    email: plima@rand.org
#    affiliations: 
#        - id: rand
#          name: RAND Corporation
#          department: Engineering and Applied Sciences
#          address: 1776 Main Street
#          city: Santa Monica
#          state: CA
#          postal-code: 90401
#    attributes:
#        corresponding: true
#  - name: and colleagues
#    email: others@rand.org
#    affiliations:
#        - ref: rand
abstract: |
  Introduces a model to assess the value provided by wastewater genomic surveillance network. This document is meant to be used as a supplementary appendix of the paper.
keywords: 
  - Genomic Surveillance
  - Pandemic Response
date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      #name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: super
  elsevier-html:
    keep-tex: true
    journal:
      #name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: super
  docx:
      cite-style: super
---

@@

Genomic surveillance might provide an early signal to decision makers by providing an early signal of prevalence, hence effectively reducing $a$.
